hbm_paper_results

### 2024-02-27 paper_main_results.Rmd
visulaizing magnitude of sex biases

>>>>

```{r}
#get range
sex_t_tests_in_feat.df %>%
  mutate(median_sex_diff = case_when(sig_fdr == FALSE ~ NA,
                              TRUE ~ median_sex_diff*100)) %>%
  group_by(dataset) %>%
  summarize(min_sex_diff = min(median_sex_diff, na.rm=TRUE),
            max_sex_diff = max(median_sex_diff, na.rm=TRUE))

#look by feature type
sex_t_tests_in_feat.df %>%
  # dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  mutate(median_sex_diff = case_when(sig_fdr == FALSE ~ NA,
                              TRUE ~ median_sex_diff*100),
         pheno_cat = factor(case_when(
    pheno %in% vol_list_global ~ "Global Volume",
    pheno %in% vol_list_regions ~ "Regional Volume",
    pheno %in% sa_list ~ "Regional SA",
    pheno %in% ct_list ~ "Regional CT",
    TRUE ~ NA_character_))) %>%
ggplot() +
  geom_histogram(aes(x=median_sex_diff, color=dataset, fill=dataset),alpha=0.5, position="identity") +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_grid(pheno_cat~dataset, scales="free")

```

### 2024-02-27 paper_prop_results.Rmd
visulaizing magnitude of sex biases

```{r}
cent.t.test.df %>%
  dplyr::filter(sig_fdr==TRUE) %>%
ggplot() +
  geom_bar(aes(x=prop, fill=bigger_group)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~comp)
```

@@

```{r}
cent.subj.sex.test.list <- readRDS(paste0(data_path, "/full_featurewise_cent_sex_bias_tests.RDS"))
cent.subj.sex.test.df <- bind_rows(cent.subj.sex.test.list)
```

@@

```{r}
cent.subj.sex.test.df %>%
  ggplot() +
  geom_bar(aes(x=prop, fill=sig_fdr)) +
  facet_wrap(~dataset) +
  scale_x_discrete(labels=percent_f) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

@@

```{r, eval=FALSE}
cent.subj.sex.test.df %>%
  mutate(median_sex_diff = case_when(sig_fdr == FALSE ~ NA,
                              TRUE ~ median_sex_diff*100)) %>%
  ggplot() +
  geom_histogram(aes(x=median_sex_diff, fill= dataset, color=dataset), alpha=0.4, position = "identity") +
  facet_wrap(~prop)

#zoom in on combat-GAM vs combat-LS
cent.subj.sex.test.df %>%
  dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  mutate(median_sex_diff = case_when(sig_fdr == FALSE ~ NA,
                              TRUE ~ median_sex_diff*100)) %>%
  ggplot() +
  geom_histogram(aes(x=median_sex_diff, fill= dataset, color=dataset), alpha=0.4, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_wrap(~prop, labeller = as_labeller(percent_f)) +
  theme(plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

cent.subj.sex.test.df %>%
  group_by(dataset, prop) %>%
  summarize(min_diff = min(median_sex_diff)*100, max_diff=max(median_sex_diff)*100)
```

@@

```{r}
#trying to add stats test
global_sex_diffs <- cent.subj.sex.test.df %>%
  dplyr::filter(pheno %in% vol_list_global & dataset %in% c("cf.gam", "cf.gamlss")) %>%
  mutate(pheno_prop = paste(pheno, prop, sep="&"))

@@

```{r, eval=FALSE}
cent.subj.sex.test.df %>%
  dplyr::filter(dataset == "cf.gamlss") %>%
  dplyr::select(pheno, prop, sig_fdr) %>%
  arrange(pheno, prop)
```

@@

cent.subj.sex.test.df2 <- cent.subj.sex.test.df %>%
  dplyr::filter(prop == "prop-04") %>%
  mutate(pheno_cat = as.factor(case_when(
    pheno %in% vol_list_global ~ "Global Volume",
    pheno %in% vol_list_regions ~ "Regional Volume",
    pheno %in% sa_list ~ "Regional SA",
    pheno %in% ct_list ~ "Regional CT",
    TRUE ~ NA_character_)),
    label = sub("_[^_]*_", "_", pheno)) #for plotting
sex_t_tests_to_plot <- left_join(cent.subj.sex.test.df2, dk.parc, by="label")

@@

comp.df %>%
  dplyr::filter(sig_fdr==TRUE) %>%
ggplot() +
  geom_bar(aes(x=comp, fill=bigger_group)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap( ~ full_df)
```
Test sex-biases in centile errors w/in each feature
```{r}
noext_cent.subj.sex.test.list <- readRDS(paste0(data_path, "/no.ext_featurewise_cent_sex_bias_tests.RDS"))
noext_cent.subj.sex.test.df <- bind_rows(noext_cent.subj.sex.test.list)
```

@@

```{r}
noext_cent.subj.sex.test.df %>%
  ggplot() +
  geom_bar(aes(x=prop, fill=sig_fdr)) +
  facet_wrap(~dataset) +
  scale_x_discrete(labels=percent_f) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

>>>>

```{r}
cent.t.test.df %>%
  dplyr::filter(sig_fdr==TRUE) %>%
ggplot() +
  geom_bar(aes(x=prop, fill=bigger_group)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~comp)

cent.t.test.df %>%
  dplyr::filter(sig_fdr==TRUE) %>%
  mutate(pheno_cat = factor(case_when(
    pheno %in% vol_list_global ~ "Global Volume",
    pheno %in% vol_list_regions ~ "Regional Volume",
    pheno %in% sa_list ~ "Regional SA",
    pheno %in% ct_list ~ "Regional CT",
    TRUE ~ NA_character_))) %>%
ggplot() +
  geom_bar(aes(x=prop, fill=bigger_group)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_grid(pheno_cat~comp, scales="free_y")
```

@@

```{r}
cent.feat.sex.test.list <- readRDS(paste0(data_path, "/full_featurewise_cent_sex_bias_tests.RDS"))
cent.feat.sex.test.df <- bind_rows(cent.feat.sex.test.list)
```

@@

```{r}
cent.feat.sex.test.df %>%
  ggplot() +
  geom_bar(aes(x=prop, fill=sig_fdr)) +
  facet_wrap(~dataset) +
  scale_x_discrete(labels=percent_f) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

@@

```{r}
cent.feat.sex.test.df %>%
  mutate(median_sex_diff = case_when(sig_fdr == FALSE ~ NA,
                              TRUE ~ median_sex_diff*100),
         pheno_cat = factor(case_when(
    pheno %in% vol_list_global ~ "Global Volume",
    pheno %in% vol_list_regions ~ "Regional Volume",
    pheno %in% sa_list ~ "Regional SA",
    pheno %in% ct_list ~ "Regional CT",
    TRUE ~ NA_character_))) %>%
  ggplot() +
  geom_histogram(aes(x=median_sex_diff, fill= pheno_cat, color=pheno_cat), alpha=0.4, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_grid(prop~dataset, scales="free")

#zoom in on combat-GAM vs combat-LS
cent.feat.sex.test.df %>%
  dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  mutate(median_sex_diff = case_when(sig_fdr == FALSE ~ NA,
                              TRUE ~ median_sex_diff*100)) %>%
  ggplot() +
  geom_histogram(aes(x=median_sex_diff, fill= dataset, color=dataset), alpha=0.4, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_wrap(~prop, labeller = as_labeller(percent_f)) +
  theme(plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

cent.feat.sex.test.df %>%
  group_by(dataset, prop) %>%
  summarize(min_diff = min(median_sex_diff)*100, max_diff=max(median_sex_diff)*100)
```

@@

```{r}
#trying to add stats test
global_sex_diffs <- cent.feat.sex.test.df %>%
  dplyr::filter(pheno %in% vol_list_global & dataset %in% c("cf.gam", "cf.gamlss")) %>%
  mutate(pheno_prop = paste(pheno, prop, sep="&"))

@@

```{r, eval=FALSE}
cent.feat.sex.test.df %>%
  dplyr::filter(dataset == "cf.gamlss") %>%
  dplyr::select(pheno, prop, sig_fdr) %>%
  arrange(pheno, prop)
```

@@

cent.feat.sex.test.df2 <- cent.feat.sex.test.df %>%
  dplyr::filter(prop == "prop-04") %>%
  mutate(pheno_cat = as.factor(case_when(
    pheno %in% vol_list_global ~ "Global Volume",
    pheno %in% vol_list_regions ~ "Regional Volume",
    pheno %in% sa_list ~ "Regional SA",
    pheno %in% ct_list ~ "Regional CT",
    TRUE ~ NA_character_)),
    label = sub("_[^_]*_", "_", pheno)) #for plotting
sex_t_tests_to_plot <- left_join(cent.feat.sex.test.df2, dk.parc, by="label")

@@

comp.df %>%
  dplyr::filter(sig_fdr==TRUE) %>%
ggplot() +
  geom_bar(aes(x=comp, fill=bigger_group)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap( ~ full_df)
```
Test sex-biases in centile errors w/in each feature
```{r}
noext_cent.subj.sex.test.list <- readRDS(paste0(data_path, "/no.ext_featurewise_cent_sex_bias_tests.RDS"))
noext_cent.feat.sex.test.df <- bind_rows(noext_cent.subj.sex.test.list)
```

@@

```{r}
noext_cent.feat.sex.test.df %>%
  ggplot() +
  geom_bar(aes(x=prop, fill=sig_fdr)) +
  facet_wrap(~dataset) +
  scale_x_discrete(labels=percent_f) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

### 2024-02-27 paper_replication_results.Rmd
visulaizing magnitude of sex biases

>>>>

```{r}
#get range
cent.subj.sex.test.df %>%
  mutate(median_sex_diff = case_when(sig_fdr == FALSE ~ NA,
                              TRUE ~ median_sex_diff*100)) %>%
  group_by(dataset) %>%
  summarize(min_sex_diff = min(median_sex_diff, na.rm=TRUE),
            max_sex_diff = max(median_sex_diff, na.rm=TRUE))

#look by feature type
cent.subj.sex.test.df %>%
  # dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  mutate(median_sex_diff = case_when(sig_fdr == FALSE ~ NA,
                              TRUE ~ median_sex_diff*100),
         pheno_cat = factor(case_when(
    pheno %in% vol_list_global ~ "Global Volume",
    pheno %in% vol_list_regions ~ "Regional Volume",
    pheno %in% sa_list ~ "Regional SA",
    pheno %in% ct_list ~ "Regional CT",
    TRUE ~ NA_character_))) %>%
ggplot() +
  geom_histogram(aes(x=median_sex_diff, color=perm, fill=perm),alpha=0.5, position="identity") +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_grid(pheno_cat~dataset, scales="free")

```
